Procedural generation of levels fot he angry birds videogame using evolutionary computation\\

### 2019-05-14 article_english.tex
Backgound checked, more writing needed

In this Section we provide a quick overview of the literature about the areas
that provide the basis to the development of the current project, this section
is divided in three parts, the fisrt one gives us an explanation of what
procedural content generation entails, the second one provides an explanation on
genetic algorithms and how can they be used to solve optimization problems, and
finally, the third one provides us with an overview of Open-Ended Evolution and
what it means to have an Open-Ended Evolutionary algorithm.

@@

Procedural content generation (PCG) denotes the way to automatically generate
content by algorithms instead of generating the same content by manual means
such as with different personnel.

@@

\begin{itemize}
    \item Level Design: This aspect involves only the design of specific
    sections of a game, primarily those in which the player is able to interact.
    \item Audio: This aspect is focused on designing soundtracks that are able
    to react to a player specific action.
    \item Visuals: This area is focused on creating or improving visual
    representations of objects on games such as giving raw designs of players
    faces of improving the images of other graphics.
    \item Narrative: This aspect is focused on the generation of readable and
    coherent stories or plotlines of games.
    \item Gameplay: This aspect uses agents to test and evaluate the mechanic on
    which a game is based by trying to play as a human would in order to improve
    said mechanics.
    \item Game Design: This aspect is focused on generating the rulesets and mechanics of a new game. \cite{Yannakakis2017}
\end{itemize}

\subsection{Genetic algorithm}
Is a method developed by John Holland on 1975 \cite{Holland1975} the genetic
algorithm (GA) is an optimization and search technique based on the principles
of genetic and natural selection, it allows a population composed of many
individuals, which by themselves represent a possible solution to the problem,
to evolve under specific selection rules in order to obtain the maximum fitness.

@@

@@

>>>>

In this Section we provide a quick overview of the literature about the areas
that provide the basis to the development of the current project, this section
is divided in three parts, the fisrt one gives us an explanation of what
procedural content generation entails, the second one provides an explanation on
genetic algorithms and how can they be used to solve optimization problems, and
finally, the third one provides us with an overview of Open-Ended Evolution and
% use just one form, I prefer with no first caps open-ended evolution and let's 
% use an abbreviation OEE - MG  
what it means to have an Open-Ended Evolutionary algorithm.

% For this conference I think we do not need to define PCG, let's think 
% every one knows what it is. - MG

@@

Procedural Content Generation (PCG) denotes the way to automatically generate
content by algorithms instead of generating the same content by manual means
such as with different personnel.

@@

% Jaime, you must add references to EVERY THING READ alsewhere : 
% We do not proposed this list, please add a reference. - MG       
\begin{itemize}
    \item Level Design: This aspect involves only the design of specific
    sections of a game, primarily those in which the player is able to interact.
    \item Audio: This aspect is focused on designing soundtracks that are able
    to react to a player specific action.
    \item Visuals: This area is focused on creating or improving visual
    representations of objects on games such as giving raw designs of players
    faces of improving the images of other graphics.
    \item Narrative: This aspect is focused on the generation of readable and
    coherent stories or plotlines of games.
    \item Gameplay: This aspect uses agents to test and evaluate the mechanic on
    which a game is based by trying to play as a human would in order to improve
    said mechanics.
    \item Game Design: This aspect is focused on generating the rulesets and mechanics of a new game. \cite{Yannakakis2017}
\end{itemize}

\subsection{Genetic algorithm}
Is a method developed by John Holland on 1975 \cite{Holland1975} % Yes ! like this - MG
the genetic
algorithm (GA) is an optimization and search technique based on the principles
of genetic and natural selection, it allows a population composed of many
individuals, which by themselves represent a possible solution to the problem,
to evolve under specific selection rules in order to obtain the maximum fitness.

@@

% Maybe this is well known, again our implementation is what we need to describe 
% JJ, what you think?

@@

% This section and the proposed approach should be in the fron lines - MG

% The problem is that we just state what it is, but we do not link it
% with our work. Why is important? What inpired our work? 
% There is also Novelty Search - MG
% Also it sounds like a copy-paste from Wikipedia please check and reference
% accordingly - MG
